### 2014-06-06 method.tex
sergio's c-cnn section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cascaded CNN}\label{sec:ccnn}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \todo{Explain training the thresholds.}
\end{itemize}

\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

>>>>

\subsection{Cascaded CNN}\label{sec:ccnn}

@@

To set the thresholds we took a sample of 140K regions from the images in the validation set containing positive and negative examples. Then we set the threshold for the rejector after first layer to have 0.8 recall on the positive regions. Similarly we set the threshold in for the rejector after the second layer, using the regions that pass the first rejector, to maintain a 0.8 recall on positive regions. And finally we set the threshold for the rejector after the third layer, using the regions that pass the first two rejectors, to maintain a 0.8 recall on positive regions. After every rejection layer the precision on positive regions increase, going from 0.38 to 0.74, while maintaining a recall of 0.8.

To estimate the saving on time by using the rejectors we timed the time spend to process 1000 regions (10 batches or 100) and the time expended in each of the first 3 layers:
\begin{itemize}
\item 1700 ms to process all the layers
\item 270 ms (15\%) in layer 1 (This includes conv1, relu1, pool1, norm1)
\item 360 ms (20\%) in layer 2 (This includes conv2, relu2, pool2, norm2)
\item 285 ms (15\%) in layer 3 (This includes conv3, relu3)
\end{itemize}

Therefore the expected ``lifetimes'' of regions rejected after layer 1, layer 2, layer 3 and those not rejected are  0.15, 0.35, 0.5, 1.0 of the total time taken per region (~1.7 ms).

At test time, I observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch. I multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.
